### 2016-08-16 latex/paper.tex
Stability equation

\section{DEFORMATION OF THE WHEEL}
\subsection{Rim equations}

@@

The in-plane curvature $\kappa_1$ is assumed to remain constant during flexural-torsional buckling. The in-plane curvature, out-of-plane curvature and twist rate are
\begin{equation}\label{eq:k1}
\kappa_1 = 1/R
\end{equation}
\begin{equation}\label{eq:k2}
\kappa_2 = u'' - \frac{\phi}{R}
\end{equation}
\begin{equation}\label{eq:k3}
\kappa_3 = \phi' + \frac{1}{R} u'
\end{equation}
The symbol $()'$ indicates a derivative with respect to $s$. It can easily be verified that Equations \ref{eq:k2} and \ref{eq:k3} simplify to the standard equations for straight beams in the limit $R\rightarrow \infty$. The curvature and twist rate produce a bending moment and twisting moment equal to
\begin{equation}\label{eq:M2}
M_2 = EI_{11} \kappa_2
\end{equation}
\begin{equation}\label{eq:M3}
M_3 = GJ \kappa_3 + EI_w \kappa_3''
\end{equation}
The total strain energy is decomposed into lateral bending, uniform torsion, and warping terms which are related to the curvatures.
\begin{equation}\label{eq:Urim}
U_{rim} = \int_0^{2\pi} \left( \frac{1}{2} EI_{22} \kappa_2^2 + \frac{1}{2} GJ \kappa_3^2 + \frac{1}{2} EI_w (\kappa_3')^2 \right)\, ds
\end{equation}
After buckling, a differential line segment $ds$ deforms to $dS$. The apparent shortening of the line segment along the $s$ direction is then
\begin{equation}\label{eq:ds}
ds - dS = ds - \sqrt{ds^2 + \left(\frac{du}{ds}ds\right)^2} \approx \frac{1}{2} (u')^2 \, ds
\end{equation}
The axial compressive force in the rim moves through this differential displacement, performing virtual work equal to
\begin{equation}\label{eq:Vrimr}
V_{rim} = \frac{1}{2} \int_0^{2\pi} N_r (u)^2 \, ds
\end{equation}

@@

Following the approach of Smith~\cite{Smith1901a} and Pippard~\cite{Pippard1932d}, we will approximate the spoke system as a continuum which exerts a distributed load on the rim. The stiffness per unit length is defined by the sum of the spoke stiffnesses in one periodic grouping of spokes, divided by the arc length of the grouping.
\begin{equation}\label{eq:kbar}
\bar{\bm{k}} = \frac{1}{2\pi R}\left(\frac{n_s}{n_p}\right) \sum_i^{n_p} \bm{k}_{f, i}
\end{equation}

\subsection{Total potential energy and buckling criterion}
The buckled shape of the wheel must be periodic, so we assume a buckled shape of the form
\begin{equation}\label{eq:modeshape}
\begin{split}
u(s) &= \delta u_n \cos{\frac{ns}{R}} \\
\phi(s) &= \delta\phi_n \cos{\frac{ns}{R}}
\end{split}
\end{equation}
The wheel becomes unstable when the increase in strain energy is exactly balanced by the virtual work for a perturbing displacement $\delta u_n, \delta\phi_n$, i.e. when
\begin{equation}\label{eq:TotPot}
U_{rim} - V_{rim} = 0
\end{equation}
Substituting the buckling mode shape Eqn. \ref{eq:modeshape} into Eqns. \ref{eq:Urim} and \ref{eq:Vrimr} and substituting into Eqn. \ref{eq:TotPot} yields the critical buckling criterion for the $n$th mode.
\begin{equation}\label{eq:Tcrit}
...
\end{equation}
\section{CONCLUSIONS}

>>>>

\section{DEFORMATION OF THE WHEEL}
...Tensegrity
\begin{equation}\label{eq:TN}
N_r = \frac{n_sT}{2\pi}
\end{equation}

\subsection{Rim equations}

@@

The in-plane curvature $\kappa_1$ is assumed to remain constant during flexural-torsional buckling. The in-plane curvature, out-of-plane curvature and twist rate are
\begin{equation}\label{eq:k1}
\kappa_1 = 1/R
\end{equation}
\begin{equation}\label{eq:k2}
\kappa_2 = u'' - \frac{\phi}{R}
\end{equation}
\begin{equation}\label{eq:k3}
\kappa_3 = \phi' + \frac{1}{R} u'
\end{equation}
The symbol $()'$ indicates a derivative with respect to $s$. It can easily be verified that Equations \ref{eq:k2} and \ref{eq:k3} simplify to the standard equations for straight beams in the limit $R\rightarrow \infty$. The curvature and twist rate produce a bending moment and twisting moment equal to
\begin{equation}\label{eq:M2}
M_2 = EI_{11} \kappa_2
\end{equation}
\begin{equation}\label{eq:M3}
M_3 = GJ \kappa_3 + EI_w \kappa_3''
\end{equation}
The total strain energy is decomposed into lateral bending, uniform torsion, and warping terms which are related to the curvatures.
\begin{equation}\label{eq:Urim}
U_{rim} = \int_0^{2\pi} \left( \frac{1}{2} EI_{22} \kappa_2^2 + \frac{1}{2} GJ \kappa_3^2 + \frac{1}{2} EI_w (\kappa_3')^2 \right)\, ds
\end{equation}
After buckling, a differential line segment $ds$ deforms to $dS$. The apparent shortening of the line segment along the $s$ direction is then
\begin{equation}\label{eq:ds}
ds - dS = ds - \sqrt{ds^2 + \left(\frac{du}{ds}ds\right)^2} \approx \frac{1}{2} (u')^2 \, ds
\end{equation}
The axial compressive force in the rim moves through this differential displacement, performing virtual work equal to
\begin{equation}\label{eq:Vrim}
V_{rim} = \frac{1}{2} \int_0^{2\pi} N_r (u')^2 \, ds
\end{equation}

@@

Following the approach of Smith~\cite{Smith1901a} and Pippard~\cite{Pippard1932d}, we will approximate the spoke system as a continuum which exerts a distributed load on the rim. The stiffness per unit length is defined by the sum of the spoke stiffnesses in one periodic grouping of spokes, divided by the arc length of the grouping.
\begin{equation}\label{eq:kbar}
\bar{\bm{k}} = \frac{1}{2\pi R}\left(\frac{n_s}{n_p}\right) \sum_i^{n_p} \bm{k}_{f, i}
\end{equation}
The distributed load $\bar{\bm{f}}$ does an amount of work per unit length equal to
\begin{equation}\label{eq:w_spokes}
\bar{w} = \int_0^{u_n} \bar{\bm{f}} \cdot d\bm{u}_n = \frac{1}{2} \bm{u}_n \cdot \bar{\bm{k}} \cdot \bm{u}_n
\end{equation}
The line of action is assumed to pass sufficiently close to the rim shear center that any difference between the displacement of the spoke nipple and the displacement of the shear center can be ignored. The total strain energy stored in the spoke system is equal to
\begin{equation}\label{eq:Us}
U_{spokes} = \int_0^{2\pi} \bar{w} \, ds = \frac{1}{2}\left( \bar{k}_{uu}u^2 + \bar{k}_{vv}v^2 + \bar{k}_{ww}w^2 + 2\bar{k}_{uv}uv + 2\bar{k}_{uw}uw + 2\bar{k}_{vw}vw\right)
\end{equation}

\subsection{Total potential energy and buckling criterion}

The buckled shape of the wheel must be periodic, so we assume a buckled shape of the form
\begin{equation}\label{eq:modeshape}
\begin{split}
u &= \delta u_n \cos{\frac{ns}{R}} \\
\phi &= \delta\phi_n \cos{\frac{ns}{R}}
\end{split}
\end{equation}
The wheel becomes unstable when the increase in strain energy is exactly balanced by the virtual work for a perturbing displacement $\delta u_n, \delta\phi_n$, i.e. when the total potential energy is zero.
\begin{equation}\label{eq:TotPot}
\Pi = U_{rim} + U_{spokes} - V_{rim} = 0
\end{equation}
Substituting the buckling mode shape Eqn. \ref{eq:modeshape} into Eqns. \ref{eq:Urim}, \ref{eq:Vrim}, and \ref{eq:Us} and substituting into Eqn. \ref{eq:TotPot} yields a buckling criterion for the $n$th mode.
\begin{multline}\label{eq:BuckCrit}
\frac{\pi EI_{11}}{R^3}(n^2 u_n - R\phi_n)^2 + \frac{\pi n^2}{R^2}\left(GJ + \frac{EI_w}{R^2}n^2\right)(u_n-R\phi_n)^2 + \\
\pi R(\bar{k}_{uu}^{el} + T\bar{k}_{uu}^{el})u_n^2 - N_r\frac{\pi n^2}{R}u_n^2=0
\end{multline}
Equation \ref{eq:BuckCrit} has a quadratic form and can be written using matrix notation:
\begin{equation}\label{eq:Qform}
\begin{bmatrix}
u_n\\\phi_n
\end{bmatrix} \cdot
\begin{bmatrix}
\frac{\partial^2 \Pi}{\partial u_n^2} & \frac{\partial^2 \Pi}{\partial u_n \partial \phi_n}\\
\frac{\partial^2 \Pi}{\partial u_n\partial\phi_n} & \frac{\partial^2 \Pi}{\partial \phi_n^2}
\end{bmatrix} \cdot
\begin{bmatrix}
u_n\\\phi_n
\end{bmatrix}
=0
\end{equation}
Non-trivial solutions of Eqn. \ref{eq:Qform} exist when the determinant of the matrix vanishes. Substituting Eqn. \ref{eq:TN} for $N_r$ and solving Eqn. \ref{eq:BuckCrit} for $T$ gives the critical spoke tension for the $n$th mode.
\begin{equation}
...
\end{equation}

\section{CONCLUSIONS}
